Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational approach

### 2016-09-15 ms_pre_post.Rmd
Some progress with exclusively pre- or post-copulatory inbreeding avoidance references

Few studies address evolution of both pre-copulatory and post-copulatory inbreeding strategies, but existing empirical studies support our model predictions. For example, @Lui2014 found evidence for pre-copulatory, but not post-copulatory inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*).

<!---  Lui    --->

<!--- start talking abou these now --->

<!--- Olsson1996; Pizzari2004; Firman2008; Bretman2009; Gasparini2011; Tuni2013; Firman2015 --->

<!--- The initial evolution of inbreeding fertilisation strategy might be further facilitated if the phenotypic expression of polyandry is caused by continuous genetic variation underlying a female's tendency for engaging in polyandry, as is expected for complex polygenic traits underlying behaviour under the fundamental assumptions of quantitative genetics [@Evans2008]. Under quantitative genetic assumptions, polyandry can therefore be conceptualised as a 'threshold trait', meaning that multiple mating is only realised above some threshold genetic value [@Lynch1998]. Expression of  --->

>>>>

Multiple studies have found evidence for female pre-copulatory inbreeding avoidance [e.g., @Lihoreau2007; @Kuriwada2011; @Kingma2013], and for post-copulatory inbreeding avoidance [e.g., @Simmons2006; @Bretman2009].

Few studies address evolution of both pre-copulatory and post-copulatory inbreeding strategies, but existing empirical studies are consistent with our model predictions. @Liu2014 found evidence for pre-copulatory, but not post-copulatory inbreeding avoidance in an experimental study of cabbage beetles (*Colaphellus bowringi*). In our model, post-copulatory

<!--- Note that females might mate multiply because first need to ensure that they get a mate at all.  \cite{Daniel2015} --->

<!---  Constraints on pre-cop: Limited kin recognition --->
